---
title: "HW 4 starter"
author: "Monica Klosin"
date: "11/19/2020"
output: word_document
---

The packages we need available for this program are: mosaic, dplyr, broom, and olsrr.  

```{r, packages}
library(mosaic)
library(dplyr)
library(broom)
library(olsrr)
library(readr)

```

We begin by reading in the data set named Golf2003.  This is a .csv file.  We create a dataframe named Golf.

```{r, data}
# read in data file
Golf<- read_csv('/Users/monicaklosin/Desktop/GoogleDocs/GVSU/Fall 2020/STA321/R-assignments/hw4/Golf2003.csv')
```

1.	Create a dummy variable named D1 for X1 = Country, where USA is given the value 1 and not USA is given the value 0

```{r, Q1}
# dummy variable
Golf$D1 <- ifelse(Golf$Country== "USA", 1, 0)
Golf$D1

```

2.	Fit the full model and save the results to an R object named FM.  

```{r, Q2}
# Full Model

Model1 = lm(Scoring~D1+Driving+Fairways+GIR+Putt+Birdie+Sand+Scrambling+Bounceback, data=Golf)
Model1
```

3.	Find all possible regression models and save the results to an R object named All.  

```{r, Q3}
# Summarize all possible regressions

ALL = ols_step_all_possible(Model1)
ALL
```

4.	Find the best 1-variable, 2-variable, etc. regression models using the best subsets and save the results to an R object named Best.  

```{r, Q4}
# Summarize best models

Best = ols_step_best_subset(Model1, metric = c("cp"))
#plot results

plot(Best)
```

5.	Use the Forward Selection procedure with penter = .05 and save the results to an R object named Forward.  

```{r, Q5}
# forward selection

Forward = ols_step_forward_p(Model1, penter = 0.05, details = TRUE)
Forward
```

6.	Use the Backward Elimination procedure with prem = .10 and save the results to an R object named Backward.  

```{r, Q6}
# backward elimination

Backward = ols_step_backward_p(Model1, prem = .10, details = TRUE)
Backward
```

7.	Use the Stepwise procedure with prenter = .05 and prem = .10 and save the results to an R object named Stepwise.  

```{r, Q7}
# stepwise

Stepwise = ols_step_both_p(Model1, prenter = 0.05, prem = .10, progress = TRUE)
Stepwise
```

8.	Fit the final model and save to an R object named FinalModel.  

```{r, Q8}
# Final Model
FinalModel = lm(Scoring~GIR+Putt+Birdie+Scrambling, data= Golf)
FinalModel
```

9.	Write the code to get the variance inflation factors for the final model.  

```{r, Q9}
# VIF
ols_vif_tol(FinalModel)
```

10.	Write the code to get a chart of the Cooks D for the final model

```{r, Q10}
# Cooks D
ols_plot_cooksd_chart(FinalModel, print_plot = TRUE)

```

11.	Write the code to make Studentized Residuals vs. Predicted.  

```{r, Q11}
# Residual v. Predicted

ols_plot_resid_stud_fit(FinalModel, print_plot = TRUE)
```


12.	Write the code to make a histogram of the studentized residuals.    

```{r, Q12}
# Histogram of Residuals
ols_plot_resid_hist(Model1, print_plot = TRUE)

xqqmath(~.std.resid, data = Model1.metrics, xlab="quantile", ylab="standardized residuals")




```









