---
title: "hw1starter.rmd"
author: "Monica Klosin"
date: "Date"
output: word_document
---

The packages we need available for this program are: mosaic and dplyr.  

```{r, packages}
library(mosaic)
library(dplyr)

```

We begin by reading in the data set named heights husband and wife.  This is a .csv file.  The R dataframe is named Heights.

```{r, data}
# read in data file
library(readr)
Heights <- read_csv('/Users/monicaklosin/Desktop/GoogleDocs/GVSU/Fall 2020/STA321/R-assignments/hw1/hw1.csv')
#View(Heights)
```

4.	Find numerical summaries for the variable Husband and Wife.  

```{r, Q4}      
# find numerical summaries
favstats(~Husband, data= Heights, na.rm=TRUE)
favstats(~Wife, data= Heights, na.rm=TRUE)

```

5.	Make histograms of the variables Husband and Wife.   

```{r, Q5}
# histograms
histogram(~Husband, data = Heights, type="count")
histogram(~Wife, data = Heights, type="count")
```

6.	Make a scatterplot with X = Husband and Y = Wife.  

```{r, Q6}
# scatterplot
xyplot(Wife~Husband, data = Heights, pch=19)
cor(Heights$Wife, Heights$Husband)
```

7.	Find the linear correlation between X = Husband and Y = Wife.   

```{r, Q7}
# find correlation coefficient
cat("r = ", cor(Wife~Husband, data = Heights))
cor.test(Wife~Husband, data = Heights)
```

10. SLR Model between Wife and Husband

```{r, SLR}
# find least-squares line


#Use the summary( ) function to get the output from Model.
RObject = lm(Wife~Husband, data = Heights)
summary(RObject)

# get anova table
anova(RObject)

```

11.	Make a scatterplot with X = Husband and Y = Wife that includes the regression line.  

```{r, Q11}
# scatterplot
xyplot(Wife~Husband, data = Heights, pch=19, type = c("p", "r"))

```

12.	Find a 99% confidence interval for the slope.  

```{r, Q12}
# C.I. on slope
confint(RObject, "Husband", level=0.99)

```

13.	Do the following intervals: 

```{r, Q13}
# confidence interval on mean of Y given X
Conf = predict.lm(RObject, interval="confidence", level = 0.97)

# prediction interval on Y given X
Pred = predict.lm(RObject, interval="prediction", level = 0.97)

#creating data frame
Int = data.frame(Heights$Husband, Conf,Pred)

#Husband 183 cm
One = Int%>%
  filter(Heights.Husband == 183)
print(One)

```

