---
title: "hw1starter.rmd"
author: "Your Name"
date: "Date"
output: word_document
---

The packages we need available for this program are: mosaic and dplyr.  

```{r, packages}
library(mosaic)
library(dplyr)

```

We begin by reading in the data set named heights husband and wife.  This is a .csv file.  The R dataframe is named Heights.

```{r, data}
# read in data file

Heights <- read.csv("/Users/monicaklosin/Desktop/Drive/GVSU/Fall 2020/STA321/hw1/heights husband and wife.csv",header=TRUE)

```

4.	Find numerical summaries for the variable Husband and Wife.  

```{r, Q4}      
# find numerical summaries
favstats(~Husband, data= Heights, na.rm=TRUE)
favstats(~Wife, data= Heights, na.rm=TRUE)

```

5.	Make histograms of the variables Husband and Wife.   

```{r, Q5}
# histograms


```

6.	Make a scatterplot with X = Husband and Y = Wife.  

```{r, Q6}
# scatterplot


```

7.	Find the linear correlation between X = Husband and Y = Wife.   

```{r, Q7}
# find correlation coefficient


```

SLR Model between Wife and Husband

```{r, SLR}
# find least-squares line


#Use the summary( ) function to get the output from Model.


# get anova table


```

11.	Make a scatterplot with X = Husband and Y = Wife that includes the regression line.  

```{r, Q11}
# scatterplot


```

12.	Find a 99% confidence interval for the slope.  

```{r, Q12}
# C.I. on slope


```

13.	Do the following intervals: 

```{r, Q13}
# confidence interval on mean of Y given X


# prediction interval on Y given X


#creating data frame


#Husband 183 cm


```

