---
title: "hw 2 starter.rmd"
author: "John Gabrosek"
date: "September 15, 2020"
output: word_document
---

The packages we need available for this program are: mosaic and dplyr.  

```{r, packages}
library(mosaic)
library(dplyr)

```

We begin by reading in the data set named ames.csv.  The R dataframe is named Ames.  Then, we select only the variables of interest for hw 2.

```{r, data}
# read in data file
# read in data file
library(readr)
Ames <- read_csv('/Users/monicaklosin/Desktop/GoogleDocs/GVSU/Fall 2020/STA321/R-assignments/hw2/ames.csv')
Ames = Ames %>% select(X1,X9,X12,X15,X16,X18,X20,Y)
View(Ames)
```

1.	Find numerical summaries of the response variable Y = SalePrice.  

```{r, Q1}
# numerical summaries of the variable Y = SalePrice
favstats(~Y, data = Ames, na.rm=TRUE)

```

2.	Make a histogram of the response variable Y = SalePrice

```{r, Q2}
# histogram of the response variable Y = SalePrice
histogram(~Y, data = Ames, type="count")

```

Transform the response to logY.

```{r, logY}
# Transform the response to logY
Ames$logY = log(Ames$Y)

```

4.	Fit the regression model saving the model output to an R Object named FullModel.    

```{r, Q4}
# Fit the regression model
Model1 = lm(logY~X1+X9+X12+X15+X16+X18+X20, data=Ames)
# Use summary() to get coefficients
summary(Model1)


```

4h.	Use the Anova function to get the anova table for the FullModel.     

```{r, Q4h}
# anova table for the FullModel


```

5.	Make a scatterplot of logY on the vertical axis and Y-hat  

```{r, Q5}
# code to add fitted values to Ames data set
Ames$FM.fitted = FullModel$fitted.values

# scatterplot of logY on the vertical axis and Y-hat


```

5 (c)	Find the value of the linear correlation between the actual logY values and FM.fitted.     

```{r, Q5c}
# linear correlation between the actual logY values and FM.fitted


```

7. Fit the regression model that has X9, X12, and X20. Save the model output to an R Object named ReducedModel

```{r, Q7}
# Fit the regression model


#anova function


```

P-Value for Partial F-Test

```{r, Q7c}
# P-Value for Partial F-Test


```