---
title: "hw 3 starter.rmd"
author: "John Gabrosek"
date: "September 18, 2020"
output: word_document
---

The packages we need available for this program are: mosaic, dplyr, and broom.  

```{r, packages}
library(mosaic)
library(dplyr)
library(broom)

```

We begin by reading in the data set named usedcars.csv.  The R dataframe is named UsedCars.  Then, we select only the variables of interest for hw 3.

```{r, data}
# read in data file
library(readr)
UsedCars <- read_csv('/Users/monicaklosin/Desktop/GoogleDocs/GVSU/Fall 2020/STA321/R-assignments/hw3/usedcars.csv')
```

1. scatterplot of Y = Price and X = Mileage


```{r, Q1}
# scatterplot of Y = Price and X = Mileage
xyplot(Price~Mileage, data = UsedCars, pch=19)

```

2.	 Make a histogram of the response variable Price.  

```{r, Q2}
# histogram of the response variable Price
histogram(~Price, data = UsedCars, type="count", breaks=seq(0, 80000, 1000))

```

Transform Y

```{r, logY}
# Transform the response to logY
UsedCars$logY = log(UsedCars$Price)

```

3.	Make a histogram of the response variable logPrice. 

```{r, Q3}
# histogram of the response variable logPrice.
histogram(~logY, data = UsedCars, type="count", breaks=seq(8, 12, .1))


```

5.	Fit Model 1 saving the model output to an R Object named Model1. Then, save the residuals to an RObject named Model1_metrics.    

```{r, Q5}
# Fit the regression model
UsedCars$X1 <- UsedCars$Mileage 
#RObject: solving linear model
#finding the Beta hat and alpha hat
#beta hat is the coefficent on millage, tells how much millage 
Model1 = lm(logY~X1, data = UsedCars)

# save the residuals

Model1.metrics = augment(Model1)
head(Model1.metrics)
#just residuals
head(Model1$residuals)
```

5. (b) Make a plot of the standardized residuals vs y-hat.      

```{r, Q5b}
# Standardized Residuals -Y-Hat Plot
xyplot(.std.resid~.fitted, data=Model1.metrics, xlab="Predicted", ylab="Standardized Residuals")

```

5. (f)	Make a normal probability plot of the standardized residuals.  

```{r, Q5f}
# normal probability plot of the standardized residuals
xqqmath(~.std.resid, data = Model1.metrics, xlab="quantile", ylab="standardized residuals")

```

6. (c)	Write the code to identify the points with high leverage and save them to an R Object named HighLev.  

```{r, Q6c}
# identify the points with high leverage
HighLev = Model1.metrics %>% filter(.hat>.00497512)
NROW(HighLev)

```

6. (d)	Make a plot of Cook’s D by observation number using the HighLev R Object.  

```{r, Q6c}
# cooks distance by observation plot, for the top five values are identified
#subset six largest Cooks D
RObject2 = Model1.metrics[order(-Model1.metrics$.cooksd),]
#HighLev = HighLev[order(-HighLev$.hat),]
plot(Model1, 4, id.n = 2) 

CooksD = Model1.metrics[order(-Model1.metrics$.cooksd),]
CooksD


```