---
title: "hw 3 starter.rmd"
author: "John Gabrosek"
date: "September 18, 2020"
output: word_document
---

The packages we need available for this program are: mosaic, dplyr, and broom.  

```{r, packages}
library(mosaic)
library(dplyr)
library(broom)

```

We begin by reading in the data set named usedcars.csv.  The R dataframe is named UsedCars.  Then, we select only the variables of interest for hw 3.

```{r, data}
# read in data file
UsedCars <- read.csv("R:/STAT/gabrosek/sta321/LM 3/usedcars.csv",header=TRUE)

```

1. scatterplot of Y = Price and X = Mileage


```{r, Q1}
# scatterplot of Y = Price and X = Mileage


```

2.	 Make a histogram of the response variable Price.  

```{r, Q2}
# histogram of the response variable Price


```

Transform Y

```{r, logY}
# Transform the response to logY


```

3.	Make a histogram of the response variable logPrice. 

```{r, Q3}
# histogram of the response variable logPrice.


```

5.	Fit Model 1 saving the model output to an R Object named Model1. Then, save the residuals to an RObject named Model1_metrics.    

```{r, Q5}
# Fit the regression model


# save the residuals


```

5. (b) Make a plot of the standardized residuals vs y-hat.      

```{r, Q5b}
# Standardized Residuals -Y-Hat Plot


```

5. (f)	Make a normal probability plot of the standardized residuals.  

```{r, Q5f}
# normal probability plot of the standardized residuals


```

6. (c)	Write the code to identify the points with high leverage and save them to an R Object named HighLev.  

```{r, Q6c}
# identify the points with high leverage


```

6. (d)	Make a plot of Cook’s D by observation number using the HighLev R Object.  

```{r, Q6c}
# cooks distance by observation plot


```